Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-19 main.Rmd
added MMPD_norm values

```{r}

>>>>

```{r}
data1  = sim_panel(nx = 2, nfacet = 3, ntimes = 500)
simulated_data <- sim_panel(nx = 2,
nfacet = 3,
ntimes = 500,
sim_dist = rep(dist_normal(seq(5, 15, 5), 5), each = 2))
data2 = simulated_data
data4 = sim_panel(nx = 2,
nfacet = 3,
ntimes = 500,
sim_dist = dist_normal(seq(5,30, 5), 5))
data3 = data2 %>% rename("temp" = "id_facet") %>% rename("id_facet" = "id_x") %>% rename("id_x" = "temp")

library(parallel)
library(gravitas)
library(hakear)

set.seed(1000)
r1 <- compute_mmpd_norm(data1, "id_x", "id_facet", response = sim_data, nperm = 200)

r2 <- compute_mmpd_norm(data2, "id_x", "id_facet", response = sim_data, nperm = 200)

r3 <- compute_mmpd_norm(data3, "id_x", "id_facet", response = sim_data, nperm = 200)

r4 <- compute_mmpd_norm(data4, "id_x", "id_facet", response = sim_data, nperm = 200)

p1 <- data1 %>%
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")

p2 <- data2 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")

p3 <- data3 %>% ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")

p4 <- data4 %>% 
  ggplot(aes(x = as.factor(id_x), y = sim_data)) + facet_wrap(~id_facet) + geom_boxplot() +xlab("")

gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD_norm:", round(r1, 3))),
                        gridExtra::arrangeGrob(p2, top = paste("MMPD_norm:", round(r2, 3))),
                        gridExtra::arrangeGrob(p3, top = paste("MMPD_norm:", round(r3, 3))),
                        gridExtra::arrangeGrob(p4, top = paste("MMPD_norm:", round(r4, 3))),
                        ncol = 2, nrow=2)
